---
title: "ADS-516 Network Analysis Midterm Coding Exercise"
author: "Dr. Suat ATAN"
date: "07 04 2021"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(eval = FALSE, include = TRUE, echo = TRUE)
```

```{r message=FALSE, warning=FALSE}
df <- read.csv("setyourname.csv")
g <- graph_from_data_frame(df)
```

**Instructions:**

-   Read all instruction carefullly.

-   Assign each result into question name:

-   Each answer will be in numeric format without digit

-   If you cannot find answer set the value NA e.g: q1 = NA

-   Last submission date: 21 April 2021

-   Late submission date: 28 April 2021 (5 point will be removed from overall score)

**Point scale:**

+-------------+--------------------------------------------------------+
| Question    | Point                                                  |
+=============+========================================================+
| 1           | 10                                                     |
+-------------+--------------------------------------------------------+
| 2           | 20                                                     |
+-------------+--------------------------------------------------------+
| 3           | 20                                                     |
+-------------+--------------------------------------------------------+
| 4           | 20                                                     |
+-------------+--------------------------------------------------------+
| 5           | 20                                                     |
+-------------+--------------------------------------------------------+
| 6           | 10                                                     |
+-------------+--------------------------------------------------------+

: Point Scale

**Questions**

Q1: Compute max degree centrality

```{r message=FALSE, warning=FALSE, paged.print=FALSE}
q1 <- YOURCODE
q1
```

Q2: Compute average degree centrality (without decimal)

```{r}
q2 <- YOURCODE
q2
```

Q3: Compute density and multiple it with 1000 and round (digits parameter should be zero)

```{r}
q3a <- YOURCODE
q3 = round(q3a*1000,digits = 0)
q3
```

Q4: Compute the average path length across network and round it with zero digit.

```{r}
q4a <- YOURCODE
q4 <- round(q4a,digits = 0)
q4
```

Q5: Compute the mininum Eigenvector centrality:

```{r}
q5<-YOURCODE
q5
```

Q6: It is challenge question you need to think about. Question is: Filter

```{r}
q6a = YOURCODE
q6 <- as.numeric(q6a)
q6
```

**Report your answers**

Run code below and copy the result and paste it into e-mail with e-mail with subject of 'MIDHASH' and send it to your instructor. And attach your .Rmd file within.

```{r}
answer_set <- c(q1,q2,q3,q4,q5,q6)
answer_set
```
